### 2020-12-25 main/intro.tex
Before applying meeting#1's comments

general field of array processing has been thoroughly studied throughout several decades.

@@

The array size and the number of its elements ($N$) have significant influence on the obtained array performance, such as SNR improvement, spatial separation capabilities and its spatial response's degrees of freedom (DOF). For example, the influential MUSIC algorithm \cite{schmidt1986multiple} enables the localization of signals arriving from up to $N-1$ distinctive directions of arrival (DOA), by projecting the array manifold onto the noise subspace.

@@

One approach, commonly referenced as ``virtual arrays'' \cite{pal2010nested,chevalier2005virtual,dogan1995applications} deals with the extraction of samples originated in sensors that do not really exist by using high (higher than 2) order statistics and manipulating multiple statistical cross-terms in order to estimate statistical characteristics of signals impinging on missing sensors.

@@

\par Pursuing other approaches to improve the array's spatial performance, ULA spatial array processing analogy to finite impulse response (FIR) \cite{van1988beamforming} and the infinite impulse response (IIR) superior performance (e.g. narrower transition regions and higher sidelobes attenuation) gave rise to the question ``what are the spatial domain processing methods which will be analogous to temporal domain IIR filtering?''
\par Achieving a spatial IIR response has also motivated other works.

@@

The first one was to estimate the time of arrival (TOA) difference between two consecutive sensors and to synthetically generate the recursive part of the IIR filter, entirely in the time-domain. The second approach suggested to consider overlapping subsets of one large ULA as a finite approximation to an infinite array. 

@@

Also, ultra-wideband (UWB) filters, which sample spatial snapshots of the signal and recursively process it in the temporal domain were designed in \cite{bruton1983highly}, using the $2D$ spatio-temporal plane wave representation as a straight line angled according to the DOA.

@@

To this end, we arbitrarily choose to formulate the problem in the context of localization, hence our goal is to estimate the direction and the range of some target of interest. 
\par The novelty, compared to traditional array processing, is the incorporation of a spatial feedback, which we prove to be the spatial domain equivalent of temporal domain IIR filtering.
Assuming the target of interest has a mirror-like behaviour (i.e. reflects its impinging signals), the spatial feedback between the array and the target is created by continuously re-transmitting a synthesized version of the impinging signal (and its reflections) to the target.

@@

\par The outline of this paper is as follows. We first formulate the classic spatial beamforming setup in Sec.~\ref{sec:setup}. Then, in Sec.~\ref{sec_introduceFeedback}, we propose our novel feedback-based architecture, and formulate its spatial response.
Searching for localization performance maximization, Sec.~ \ref{sec_FIM} discusses the information-theory related considerations for the array configuration, utilizing the Fisher Information Matrix (FIM) in the context of the target's range and DOA estimation.
In Sec.~\ref{sec_Performance}, we evaluate some key features of the proposed beamforming with feedback. Specifically, we compute the array beamwidth, its peak-to-sidelobe ratio and the array directivity, showing significant improvement compared to traditional beamforming without spatial feedback. 
In Sec.~\ref{sec_app}, we simulate the proposed processing scheme, and emphasize its sensitivity to range errors. We then suggest a strategy which mitigates this sensitivity. Finally, concluding remarks are given in Sec.~\ref{sec_conclusions}.

>>>>

\chapter{Introduction}
\label{chap:intro}
The general field of array processing has been thoroughly studied throughout several decades.

@@

The array size and the number of its elements ($N$) has significant influence on the obtained array performance, such as SNR improvement, spatial separation capabilities and its spatial response's degrees of freedom (DOF). For example, the influential MUSIC algorithm \cite{schmidt1986multiple} enables the localization of signals arriving from up to $N-1$ distinctive directions of arrival (DOA), by projecting the array manifold onto the noise subspace.

@@

One approach, commonly referenced as ``virtual arrays'' \cite{pal2010nested,chevalier2005virtual,dogan1995applications} deals with the extraction of samples originated in sensors that do not really exist by using high (higher than 2) order statistics and manipulating multiple statistical cross-terms in order to estimate statistical characteristics of signals impinging in missing sensors.

@@

\par Pursuing other approaches to improve the array's spatial performance, ULA spatial array processing analogy to finite impulse response (FIR) \cite{van1988beamforming} and the infinite impulse response (IIR) superior performance (e.g. narrower transition regions and higher sidelobes attenuation) gave rise to the question ``what are the equivalent spatial domain processing methods which will be analogous to temporal IIR filtering?''
\par Achieving spatial IIR response has also motivated other works.

@@

The first one was to estimate the time of arrival (TOA) difference between two consecutive sensors and to synthetically generate the recursive part of the IIR filter, entirely in the time-domain. The second approach suggested to consider overlapping subsets of one large ULA as finite approximation to an infinite array. 

@@

Also, ultra-wideband (UWB) filters, which sample spatial snapshots of the signal and recursively process it in temporal domain were designed in \cite{bruton1983highly}, using the $2D$ spatio-temporal plane wave representation as a straight line angled according to the DOA.

@@

To this end, we arbitrarily choose to formulate the problem in the context of a localization problem, hence our goal is to estimate the direction and the range of some target of interest. 
\par The novelty, compared to traditional array processing, is the incorporation of spatial feedback, which we prove to be the spatial domain equivalent of temporal domain IIR filtering.
Assuming the target of interest has a mirror-like behaviour (i.e., reflects its impinging signals), the spatial feedback between the array and the target is created by continuously re-transmitting a synthesized version of the impinging signal (and its reflections) to the target.

@@

% \par The outline of this paper is as follows. We first formulate the classic spatial beamforming setup in Sec.~\ref{sec:setup}. Then, in Sec.~\ref{sec_introduceFeedback}, we propose our novel feedback-based architecture, and formulate its spatial response.
% Searching for localization performance maximization, Sec.~ \ref{sec_FIM} discusses the information-theory related considerations for the array configuration, utilizing the Fisher Information Matrix (FIM) in the context of the target's range and DOA estimation.
% In Sec.~\ref{sec_Performance}, we evaluate some key features of the proposed beamforming with feedback. Specifically, we compute the array beamwidth, its peak-to-sidelobe ratio and the array directivity, showing significant improvement compared to traditional beamforming without spatial feedback. 
% In Sec.~\ref{sec_app}, we simulate the proposed processing scheme, and emphasize its sensitivity to range errors. We then suggest a strategy which mitigates this sensitivity. Finally, concluding remarks are given in Sec.~\ref{sec_conclusions}.

### 2020-12-25 main/prelims.tex
Before applying meeting#1's comments

In this chapter, we overview the theoretical basis of the thesis. 
In section 1...
In section 2...
In section 3...

\begin{definition}
The \emph{von Neumann model} of a computer, also known as the \emph{Princeton architecture} is an architecture for digital computers, which consists of a processing units, containing an ALU and processing registers; a control unit consisting of an instruction register and a program counter; a memory unit which stores both data and instructions; and input-and-output mechanisms.
\end{definition}

\section{Propagating Wave Fields}
\label{sec:prlm_propWaveField}
\input{Modules/sec_prlm_propWaveField}
\section{Sensor arrays}
\label{sec:prlm_sensorArrays}
\input{Modules/sec_prlm_sensorArrays}
\section{Time-Space Signals}
\label{sec:prlm_timeSpaceSig}
\input{Modules/sec_prlm_timeSpaceSig}
\section{Sensor array performance measure}
\label{sec:prlm_sensorArrayPerf}
\input{Modules/sec_prlm_arrPerf}
\section{Finite Impulse Response Based Spatial Filtering}
\label{sec:prlm_FIR}
\input{Modules/sec_prlm_FIR}
\section{Infinite Impulse Response Filters}
\label{sec:prlm_IIR}
\section{Fisher Information Matrix}
\label{sec:prlm_FIM}

Let's define some concept we'll be using throughout the thesis.

>>>>

As a preliminary discussion to the presentation of out contribution, we overview some the key theoretical basis of the thesis.
In Sec.~\ref{sec:prlm_propWaveField}, the wave propagation, being the most basic concept for array processing, is discussed.
It is then followed by a short overview of array-processing in Sec.~\ref{sec:prlm_sensorArrays}.
To accommodate the discussion for spatial filtering, we also mention the time-space relation of spatially sampled signals in Sec.~\ref{sec:prlm_timeSpaceSig}.
As an additional theoretical concept, arriving from the information theory, which will be used in the main chapter (Ch.~\ref{chap:firstchap}), is the Fisher Information Matrix, covered in Sec.~\ref{sec:prlm_FIM}.
\par 
For an easier reading treat each section as independent, where notations and symbols are each defined in the specific section and are not mutual, nor used in the main chapter.

% \begin{definition}
% The \emph{von Neumann model} of a computer, also known as the \emph{Princeton architecture} is an architecture for digital computers, which consists of a processing units, containing an ALU and processing registers; a control unit consisting of an instruction register and a program counter; a memory unit which stores both data and instructions; and input-and-output mechanisms.
% \end{definition}

\section{Propagating Wave Fields}
\label{sec:prlm_propWaveField}
\input{Modules/sec_prlm_propWaveField}
% \section{Digital Filter Design - Finite/Infinite Response Filters}
% \label{sec:prlm_FILTERS}
% \input{Modules/sec_prlm_FILTERS}
\section{Sensor arrays}
\label{sec:prlm_sensorArrays}
\input{Modules/sec_prlm_sensorArrays}
\section{Time-Space Signals}
\label{sec:prlm_timeSpaceSig}
\input{Modules/sec_prlm_timeSpaceSig}
% \section{Sensor array performance measure}
% \label{sec:prlm_sensorArrayPerf}
% \input{Modules/sec_prlm_arrPerf}
\section{Fisher Information Matrix}
\label{sec:prlm_FIM}
\input{Modules/sec_prlm_FIM}
